\documentclass{muratcan_cv}
\setname{Walter Catalfamo}{}
\setaddress{Nice, France}
\setmobile{+33 7 66 62 90 15}
\setmail{cata.walter@gmail.com}
\setlinkedinaccount{https://www.linkedin.com/in/walter-catalfamo/} 
\setgithubaccount{https://github.com/cataWalter} 
\setthemecolor{MidnightBlue} 
\begin{document}
\headerview
\vspace{1ex}
\section{Education}
\datedexperience{Master's Degree in Computer Engineering}{Sep 2020 - Jan 2023}
\explanation{Politecnico di Milano}{Milan, Italy}
\datedexperience{Bachelor's Degree in Computer Engineering}{Sep 2017 - Jul 2020}
\explanation{Politecnico di Milano}{Milan, Italy}
\section{Skills}
\newcommand{\skillone}{\createskill{Languages}{Python \cpshalf Java \cpshalf C++ \cpshalf SQL \cpshalf PHP}}
\newcommand{\skilltwo}{\createskill{Backend Development}{Apache Kafka \cpshalf Hibernate \cpshalf Node.js}}
\newcommand{\skillthree}{\createskill{Databases}{MongoDB \cpshalf Couchbase \cpshalf MySQL}}
\newcommand{\skillfour}{\createskill{Cloud \& DevOps}{Docker \cpshalf Kubernetes \cpshalf Microsoft Azure}}
\createskills{\skillone, \skilltwo, \skillthree, \skillfour}
\section{Experience}
\datedexperience{Amadeus}{2023 - Present}
\explanation{Backend Developer}{Nice, France}
\explanationdetail{
    \smallskip
    I was part of the team that developed RESTful APIs for a distributed, cloud-native data management system running on Azure. I used Quarkus and Java, always keeping performance, security, and scalability in mind. For data persistence, I worked hands-on with NoSQL databases – specifically Couchbase. I also integrated our system with Kafka to enable event-driven communication. I handled deploying and managing our applications on Kubernetes. I used Helm charts and Argo CD, following GitOps principles to keep things consistent. We used Istio service mesh, and I got really involved with its traffic management features, mTLS encryption, and the observability tools (like distributed tracing and metrics). In addition to my development work, I also took on the role of Scrum Master within our SAFe framework, helping the team stay organized and productive.
}
\smallskip
\datedexperience{Politecnico di Milano}{Sep 2021 - Feb 2023}
\explanation{Teacher Assistant}{Milan, Italy}
\explanationdetail{
    \smallskip
    \coloredbullet\
    Led lab sessions and graded assignments for the \emph{Probability and Statistics} course.
    \smallskip
    \\\coloredbullet\
    Co-taught fundamental programming concepts in C and MATLAB for the \emph{Foundations of Computer Science} course.
}
\datedexperience{Private Tutoring}{Sep 2019 - Present}
\explanationdetail{
    \smallskip
    Provide private tutoring in advanced subjects across Math, Physics, Electronics, and Computer Science.
}
\smallskip
\datedexperience{UniTrekking}{Oct 2021 - May 2023}
\explanation{Mountain Guide}{Milan, Italy}
\explanationdetail{
    \smallskip
    Responsible for leading groups on treks in the Alps, developing strong leadership and social skills. Responsible for leading groups on treks in the Alps, developing strong leadership and social skills.
}
\smallskip
\section{Notable Projects}
\datedexperience{Skillogue}{2022}
\explanation{Full-Stack Social Network}{Personal Project}
\explanationdetail{
    \smallskip
    \coloredbullet\
    Developing a social network from the ground up to connect people based on shared hobbies and passions, managing the project from conception to deployment.
    \smallskip
    \\\coloredbullet\
    \textbf{Tech Stack:} Flutter and Dart for the cross-platform mobile front-end, with Supabase providing the backend-as-a-service for database and user authentication.
}
\datedexperience{NikiTranslator}{2022}
\explanation{Multi-Language Learning App}{Personal Project}
\explanationdetail{
    \smallskip
    \coloredbullet\
    Built a translator app that translates sentences into multiple languages simultaneously and helps users learn by tracking their most frequently used words in a personal dictionary.
    \smallskip
    \\\coloredbullet\
    \textbf{Tech Stack:} Developed as a desktop application in Python.
}
\datedexperience{Schema Query Reverse Engineering}{2022}
\explanation{Data Engineering Tool}{Academic Project}
\explanationdetail{
    \smallskip
    \coloredbullet\
    Designed and implemented an algorithm to reverse-engineer a database's schema mapping based on a series of query outputs.
    \smallskip
    \coloredbullet\
    \textbf{Tech Stack:} Core logic implemented in Python.
}
\section{Languages}
\indent
\explanationdetail{
    \smallskip
    \\\coloredbullet\
    \textbf{Native:} Italian, Sicilian
    \smallskip
    \\\coloredbullet\
    \textbf{Fluent:} English, French, Spanish
    \smallskip
    \\\coloredbullet\
    \textbf{Conversational:} Portuguese
    \smallskip
    \coloredbullet\
    \textbf{Basic:} Dutch, German, Turkish}
\end{document}